One more attempt on ArXe

### 2015-03-25 intro.tex
take care of utf8 and no linebreak within one specific citation key

Most recently, on the experimental side photoelectron spectra of 
small Ar-Xe clusters were analyzed, adding to the findings in 
earlier work.\cite{Lindblad} We will discuss this paper in 
connection with our results below. Theoretical work on Ar-Xe was 
also published, and had a focus on the radiationless decay of Ar 
inner valence vacancies in these systems.\cite{fasshauer,fasshauer
_b} Interestingly, it was found that Ar 3s$^{-1}$ is stable 
against autoionization in an ArXe dimer, but is destabilized by 
adding further Xe atoms, or an Ar solvation shell, to the system. 
Again, we will detail these results in conjunction with our 
current work.

>>>>

Most recently, on the experimental side photoelectron spectra of 
small Ar-Xe clusters were analyzed, adding to the findings in 
earlier work.\cite{Lindblad} We will discuss this paper in 
connection with our results below. Theoretical work on Ar-Xe was 
also published, and had a focus on the radiationless decay of Ar 
inner valence vacancies in these systems.\cite{fasshauer,Fasshauer13}
Interestingly, it was found that Ar 3s$^{-1}$ is stable 
against autoionization in an ArXe dimer, but is destabilized by 
adding further Xe atoms, or an Ar solvation shell, to the system. 
Again, we will detail these results in conjunction with our 
current work.
